Proxy check
========================================================

Let's check the original proxy files against the resulting averaging/aggregating using our stage bins.

RED = Original
BLUE = Aggregated into Stagetime File

There will be some jiggling due to dates being a little different from file to file.

```{r}
library(scales)
#stageTime <- read.csv("../data/cleanProxiesByStage_20131203.csv")
stageTime <- read.csv("../data/cleanProxiesByStage_20131210.csv")


#check against Hannisdal and Peters
proxy<-read.csv("../data/Hannisdal and Peters data with stage IDs.csv", na.strings="?")


for(prox in names(proxy)[14:17]){
  plot(proxy$bottom, proxy[[prox]], pch=19, col=alpha("red", 0.5), ylab=prox)
  matplot(stageTime$Start..Ma., stageTime[[prox]], pch=19, col=alpha("blue", 0.5), add=T)
}
```

H&P: Mostly good.

How about extinction rates?

```{r}
######extinction rate
extMag<-read.csv("../data/Ext mag 3-15 Revised.csv")
extMag2<-read.csv("../data/Biv BC ext PBDB 4-17-12.csv")

names(extMag2)[6]<-paste(names(extMag2)[6], "PBDB", sep=".")

#add times
extMag$Base_bottom..Ma. <- c(0,extMag$Base..Ma.[-nrow(extMag)])
extMag2$Base_bottom..Ma. <- c(0,extMag2$Base..Ma.[-nrow(extMag2)])

plot(extMag$Base_bottom..Ma., extMag$BC.extinction.rate, pch=19, col=alpha("red", 0.5), 
     ylab="Ext")
matplot(stageTime$Start..Ma., stageTime$BC.extinction.rate, pch=19, col=alpha("blue", 0.5), 
      add=T)

########PBDB
plot(extMag2$Base_bottom..Ma., extMag2$BC.extinction.rate.PBDB, pch=19, col=alpha("red", 0.5), 
     ylab="Ext")

matplot(stageTime$Start..Ma., stageTime$BC.extinction.ratePBDB, pch=19, 
        col=alpha("blue", 0.5), add=T)

```

Hrm.  The lack of peaks in the aggregated files is a bit troubling.  Worth digging into, or do we think this is OK?

The nearer point - the Maastrictian - is of a different length in the stageTime file, and thus encompasses other extinction rates, which lowers the point.
The further unmatched point - the Changhsingian in the PBDB extinction rate file - is also wider in the stageTime file, and thus is a lower extinction rate.


On to sealevel.

```{r}
########sealevel
sealevel<-read.csv("../data/Sea level residuals after 2nd-order polynomial fit.csv")

for(prox in names(sealevel)[10:11]){
  plot(sealevel$Time..my., sealevel[[prox]], pch=19, col=alpha("red", 0.5), ylab=prox)
  matplot(stageTime$Start..Ma., stageTime[[prox]], pch=19, col=alpha("blue", 0.5), add=T)
}
```


The sealevel data syncs just fine.

Onto the Prokoph proxies.
```{r}

proxyProk<-read.csv("../data/Prokoph_data_9.2013.csv")
proxyProk <- subset(proxyProk, proxyProk$data_subset=="tropical no benthics")
names(proxyProk)[6:17] <- paste(names(proxyProk)[6:17], "prok", sep=".")

for(prox in names(proxyProk)[6:17]){
  plot(proxyProk$Binned_bottom, proxyProk[[prox]], pch=19, col=alpha("red", 0.5), ylab=prox)
  matplot(stageTime$Start..Ma., stageTime[[prox]], pch=19, col=alpha("blue", 0.5), add=T)
}

```

We're so on here that the points are PURPLE.  That's because the Prokoph data uses stage names.

Last, sealevel variables
```{r}
sealevel<-read.csv("../data/Sea level residuals after 2nd-order polynomial fit.csv")

for(prox in names(sealevel)[2:11]){
  plot(sealevel$Time..my., sealevel[[prox]], pch=19, col=alpha("red", 0.5), ylab=prox)
  matplot(stageTime$Start..Ma., stageTime[[prox]], pch=19, col=alpha("blue", 0.5), add=T)
}

```
