RMA Outputs
========================================================
  
  Here we go...


```{r, echo=FALSE, include=FALSE}
read_chunk("./final_for_paper.R")
read_chunk("./plot_effect_sizes.R")
```

```{r prep, echo=FALSE, include=FALSE}
```


```{r loadData, echo=FALSE, include=FALSE}
```

```{r ploteffLoad, echo=FALSE, include=FALSE}
```



Broad v. Narrow Baseline
========================================================

First, we have to verify our assumptions about pooling all of the data.

Does grouping matter?
```{r BroadTaxaB}
```


Does Multistage matter?
```{r BroadMultStages}
```

Does Global v. Regional matter?
```{r BroadGlobalRegional}
```

Does Time Matter?
```{r BroadTime}
```

If we pool everything, what is our grand mean Log Odds Ratio for Broad v. Narrow?
```{r BroadMeanRma}
```

Figure 1
========================================================
```{r Fig1}
```



Epifauna v. Infauna Baseline
========================================================
  
Are Bivalves or Gastropods Different?
```{r bivalvesGastroHabit}
```
No - they are broadly the same.


Does global v. regional extinction matter?
```{r BroadGlobalRegionalHabit}
```

Does time matter?
```{r epiTime}
```

If we pool everything, what is our grand mean Log Odds Ratio for Epifaunal v. Infaunal?
```{r Epifaunal_rma}
```

Figure 2
========================================================
```{r Fig2}
```


Modeled Results
========================================================
The Fitted Model for Broad v. Narrow
```{r bigBroadModelRMA}
```

The Fitted Model for Epifauna v. Infauna
```{r epibigEpifaunaModel.RMA}
```

Figure 4
========================================================
```{r Fig4, fig.height=5, fig.width=9}
```

Figure 5
========================================================
```{r Fig5, fig.height=6, fig.width=15.5}
```


Appendix Jackknife Figures
========================================================
```{r jackknife.figs, echo=FALSE, warning=FALSE}
```

```{r funnelPlots, warning=FALSE}
```
